\section{Conclusions and Future Work}
\label{sec:conclusion}

Gradient-based optimization of satellite constellations has been considered intractable due to the discrete, non-differentiable nature of coverage and revisit objectives.
We showed that this intractability is an artifact of the objective formulation: by introducing four continuous relaxations and composing them with the differentiable dSGP4 orbit propagator, the entire pipeline becomes amenable to first-order optimization.
The key insight is that true analytical gradients through relaxed objectives produce a well-conditioned loss landscape, whereas the finite-difference gradients through discrete objectives used in prior work~\citep{paek2019recon} do not.

The relaxed combined objective $\mathcal{L} = -\bar{C} + \lambda\,\bar{\Delta}^{\max}$ approximates the discrete objective $\mathcal{L}_{\text{hard}} = -\bar{C}_{\text{hard}} + \lambda\,\bar{\Delta}_{\text{hard}}^{\max}$, where $\bar{C}_{\text{hard}}$ is the fraction of space-time grid cells with at least one satellite above the elevation threshold, and $\bar{\Delta}_{\text{hard}}^{\max}$ is the mean over ground points of the true maximum revisit gap.
As shown in \secref{sec:relaxation_quality}, the two objectives track closely in practice: the relaxed coverage closely matches its discrete counterpart, while the relaxed revisit provides a consistent overestimate due to the incomplete-reset and LogSumExp biases.
Crucially, optimizing the relaxed surrogate yields solutions that are near-optimal under the hard objective, validating the composed relaxation as a faithful proxy.

The framework naturally supports non-uniform, mission-specific objectives via target weighting---a problem class where parametric constellation families are fundamentally inapplicable.
On weighted target optimization for wildfire monitoring and maritime domain awareness scenarios, the optimizer discovers asymmetric geometries tailored to the target distribution, outperforming symmetric Walker-delta baselines on the mission-specific metrics while converging in 300 iterations versus thousands of evaluations for metaheuristic methods.

\paragraph{Limitations.}
The current approach optimizes a single-epoch snapshot and does not account for long-term perturbations (J2 RAAN drift, atmospheric drag) that alter constellation geometry over months.
The time step discretization introduces approximation error in the revisit metrics.
While the loss landscape appears smooth near our solutions, we cannot rule out the existence of better local minima elsewhere in the parameter space.
The discrete design variables (number of planes, satellites per plane) remain non-differentiable and must be set by the user or searched over separately.

\paragraph{Future work.}
Several extensions are natural.
Incorporating J2 secular perturbations would enable optimization of long-term constellation maintenance, potentially discovering geometries that exploit RAAN drift for improved coverage evolution.
Multi-objective Pareto optimization would allow explicit trade-offs between competing mission requirements.
Temperature annealing curricula---starting with large $\tau$ and $\tau_r$ and progressively tightening---could improve final solution quality.
Finally, the framework could be extended to constellation augmentation problems, where new satellites are optimized to complement an existing fleet, a setting that completely breaks the symmetry assumptions of parametric design families.
